Carbon cathodes for rechargeable aluminium-ion batteries

### 2019-12-16 manuscript.tex
Updates from Overleaf

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{upgreek}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{subfig}
\usepackage[version=4]{mhchem}
\onehalfspacing
\graphicspath{figures/}

\title{Carbon cathodes for rechargeable aluminium-ion batteries}

\author{
  Shalini Divya\\
  School of Chemical and Physial Sciences\\
  Victoria University of Wellington\\
  Wellington, New Zealand\\
  \texttt{shalini.divya@vuw.ac.nz}\\
  %% examples of more authors
   \And
  Thomas Nann\thanks{Corresponding author.}\\
  School of Mathematical and Chemical Sciences\\
  The University of Newcastle\\
  Newcastle, NSW 2308, Australia\\
  \texttt{thomas.nann@newcastle.edu.au}\\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
\maketitle
\begin{abstract}
 In this work, we compare four different forms of carbon: activated carbon from human hair (ACH), hemp fibers, a fullerene extract (CFEx) and Super-P carbon black as cathodes for non-aqueous aluminium-ion batteries. These materials differ in their general structure, porosity and morphology. The fullerenes display a crystalline structure, whereas hemp fibers, Super-P and ACH are amorphous in nature. Of all materials, ACH recorded the highest specific capacity after 50 cycles at 103 mAh g$^-{^1}$ with a coulombic efficiency of ~90\% at a current rate of 50 mV s$^-{^1}$. Both hemp fibers and SPC achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^-{^1}$ respectively. CFEx, a mixture of \ce{C60} (85\%) and \ce{C70} (15\%) fullerene, recorded its highest capacity at 78 mAh g$^-{^1}$ and maintained it for 50 cycles. The cells were charged and discharged to 2.45 V and 0.2 V respectively. \end{abstract}
% keywords can be removed
\keywords{carbon-based cathodes \and aluminium-ion battery \and ionic liquid \and human hair \and fullerene extract \and hemp fibers \and Super-P}
\section{Introduction}
Different varieties of carbon-based materials have been widely used in energy storage applications. Graphite, with its layered structure turned out to be an ideal intercalation cathode \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}. Activated carbon, owing to its porous structure, provided a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011}. Aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and aim to provide higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium. Exhaustive use of lithium and cobalt in LIBs would make portable batteries expensive in the coming years. One needs to switch to cost-effective alternatives. The above-mentioned properties make AIBs an interesting alternative\cite{ambroz_trends_2017-1}. We tested a number of rechargeable AIBs using an ionic liquid electrolyte with carbon-based cathodes.
Graphite has been commonly used as a cathode in AIBs. It has a) a layered structure that enhances the intercalation process, b) good conductivity and c) a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V. Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, which showed specific capacities ranging from 60-250 mAh g$^-^1$. The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge. X-ray diffraction (XRD) and Raman spectroscopy studies have widely been used to establish this mechanism\cite{rani_fluorinated_2013, wang_advanced_2017, lin_ultrafast_2015} as shown in Figure \ref{SF:graphitemech}. Raman data showed that conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicated two stages of intercalation. XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively\cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/graphitemech}
    \caption{Intercalation of AlCl$_4^_$ ions while cell charging and deintercalation during discharge in a \textbf{Al/graphite} cell. The interlayer distance between two graphite sheets is 3.3 $\AA$.}
  \label{SF:graphitemech}
\end{figure}
In this study, we compared four carbon-based materials with carbonised natural products. Super-P carbon has been used consistently as an additive to overcome any conductivity loss an active material suffers when a polymer binder such as PVDF, is added to it. Using it as an active material, we tried to find if Super-P contributes any capacity of its own to the battery's specific capacity. Activated carbon from natural products like rice or wood have been previously used in super-capacitors\cite{hussain_development_2019, frackowiak_carbon_2001}. Also known as 'hierarchical porous carbons', these structures contained pores of various sizes (mesopores and micropores), which enhanced the charge storage capacity by increasing the surface area of the electrodes . The pores absorb the charge carriers reversibly on their surface. Based on this hypothesis, we used activated carbon from human hair and hemp fibers as cathodes and got some interesting results. 

@@

\begin{table}[tbh!]
\caption{Comparing average battery metrics of all carbon cathodes} \label{table1}
\begin{threeparttable}
\begin{center}
\begin{tabular}{lcccc}
\headrow
\hline
\thead{Active material} & \thead{\textbf{Size (pore size)}} & \thead\textbf{Specific capacity (mAh g$^-^1$)} & \thead\textbf{Cell efficiency (\%)} & \thead{\textbf{Cell voltage (V)}}\\
\hline
Activated carbon from human hair & 5\mu m & 102 & 97 & 1.9 \\
Fullerene extract & 8.8\AA & 78 & 85 & 1.7 \\
Hemp fibers & 2.3 \mu m & 49 & 75 & 1.8 \\
Super-P & 300\AA & 46 & 40 & 1.5 \\
\hline  % Please only put a hline at the end of the table
\end{tabular}
\end{center}

%\begin{tablenotes}
%\item JKL, just keep laughing; MN, merry noise.
%\end{tablenotes}
\end{threeparttable}
\end{table}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CDCall}
    \caption{Specific capacities in the a) 1$^s^t$ and b) 50$^t^h$ cycle of ACH, hemp fibers, CFEx and Super-P cathodes at a current rate of 50 mA g$^-{^1}$. c) Cell efficiencies of cells at a current rate of 50 mAg$^-^1$. d) Specific capacities of carbon cells at current rates of 25 mAg$^-^1$, 50 mAg$^-^1$ and 100 mAg$^-^1$ in a two-electrode setup against \ce{Al^{3+}}/Al. }
  \label{figures:CDCall}
\end{figure}
Our battery system comprised of a cathode, 99\% pure aluminium foil as an anode and a room temperature ionic liquid (RTIL) acting as the electrolyte. ACH, hemp fibers and Super-P had an amorphous structure, however Raman spectra showed presence of a few graphitic planes. Any number of graphite-like layers would allow \ce{AlCl4-} ions to intercalate when the cell was charged. However, CFEx, a mixture of \ce{C60} and \ce{C70} fullerenes, had a crystalline lattice. Intercalation into the fullerene cage was not feasible because it needed a high amount of energy to break a C-C bond. We suggest that \ce{AlCl4-} anions seeped through the gaps present in between fullerenes without altering the molecular structure. Using a Neware BTS 3000 battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^-^1$ in Figure\ref{figures:CDCall}a and b. Structural changes in the cathode before and after cycles was studied using their Raman spectra, XRD spectra and scanning electron microscopy (SEM) images.
ACH cells recorded the highest capacity at 102-mAh g$^-{^1}$ and maintained it for 50 cycles. Coulombic efficiency was stable at ~95$\%$. Porous structure gave the material a high surface area that lead to an additional surface-based charge storage mechanism (observed in capacitors).Hemp fibers, due to their porous structure, observed a similar mechanism. Hemp cell showed a capacity of 56 mAh g$^-{^1}$ in its first cycle, which decreased to 45 mAh g$^-{^1}$ after 50 cycles. 
CFEx cell recorded its first discharge capacity at 79 mAh g$^-{^1}$, which shifted to just 78 mAh g$^-{^1}$. The cell maintained its coulombic efficiency at ~90$\%$. 
Specific capacity of the Super-P cell decreased considerably after repeated charge/ discharge cycles. With an initial capacity of 84 mAh g$^-^1$, the value decreased to 47 mAh g$^-{^1}$ with a low coulombic efficiency of $\sim$40$\%$. 
A low coulombic efficiency, which was also observed in the hemp cell, can be attributed to degradation of cathode structure, also known as cathode pulverisation. It seems due to continuous cycling, weak bonds existing between sections of the cathode broke and agglomerated into smaller chunks of C atoms. As a result, the number of surface pores decreased, which reduced the cell's capacity (Figure \ref{figures:CDCall}c). 
Human hair has two components- cuticle and cortex. One way to make carbon porous is by treating it with an activating agent. Using activating agents especially alkali hydroxides improves the porosity and increases the surface area of material \cite{liu_hair-based_2017} .
In this work, sodium hydroxide (NaOH) was used as the activating agent, which breaks the weak interactions existing between the overlapping cells in the cortex. The reaction that takes place inside the matrix after adding NaOH is:
\begin{center}
    \\4NaOH + C \longrightarrow 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{qian_human_2013}
\end{center}

NaOH was reduced to Na, these atoms in turn expanded the carbon matrix. Oxidation of carbon formed \ce{CO2}, which created pores. An increase in temperature lead to Na activation, which was later removed from the matrix via channels created by \ce{CO2}. The channels created in this process provided path for \ce {AlCl4-} to intercalate inside the pores. The activating agent:carbon ratio and the calcinating temperature played an important role in determining the size of pores. The calcinating temperature used here was 750$^{\circ}$C. A schematic of ACH synthesis has been described in Figure \ref{SF:ACHsyn}. Dong \textit{et al.} suggested that at higher temperatures (>900$^{\circ}$C) pores start to collapse resulting in graphitic sheets \cite{dong_commercial_2019}. 
Fibers obtained from Hemp (\textit{Cannabis Sativa L.}) have been used in several commercial items including paper, textiles, clothing, biodegradable plastics, paints, and bio-fuels. They have been used as reinforcements in composite materials and are capable of replacing glass fibers. Hemp fibers have a high moisture content which can be removed after high temperature treatment\cite{hussain_development_2019}. For creating activated carbon from these fibers, potassium hydroxide (KOH) was used as the activating agent. Since the samples were obtained from Carbon Valley\textsuperscript{\textregistered}, we are unable to report the precise calcinating temperature used. Unfortunately the structural domains appeared to have been damaged after this process. This phenomena negatively impacted its charge-storing capacity.  
Fullerenes have a fused-ring structure. The nucleus-to-nucleus diameter is 7.1\AA\ and van der Waals diameter is 11\AA\ in a single crystal. Presence of $\pi$-electrons on its surface makes it a good electron acceptor. However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or a long-range conductivity\cite{loutfy_fullerene_2002, winkler_two-component_2007}. Electrochemical reduction of \ce{C60} to \ce{C60^{-3}} is highly reversible suggesting they are capable of giving reversible capacities. However, they are weak battery cathode materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}. To test their solubility in \ce{AlCl3}-EMImCl ionic liquid, 100 mg of CFEx was mixed in the electrolyte and stirred for 4 hours. For comparison, we mixed hemp fibers in another vial. The vials were left to stand for 24 hours in a \ce{N2}-filled glove box. A phase separation was observed with hemp fibers but not for CFEx indicating it dissolved in the electrolyte (Figure \ref{SF:CFExsol}. It has been reported in Li-S batteries that poly-sulphides produced during charge-discharge were soluble in the electrolyte. It forms an insulating layer of \ce{Li2S} on the anode, which resulted in capacity fading \cite{sun_effect_2017, yan_2d_nodate}. However, reversible capacities obtained after 50 cycles suggested no such molecules were formed with \ce{AlCl3}/EmImCl electrolyte. 
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/superPmech}
    \caption{Suggested mechanism for a \textbf{Al/Super-P} cell. Super-P has a very amorphous structure with a few graphite-like planes present in it. AlCl$_4^_$ ions intercalate into those layers and give the cell its capacity. However, cathode pulverisation results in capacity fading.}
  \label{figures:superPmech}
\end{figure}
Pore size for Super-P ranges from ~30-50 nm \cite{younesi_analysis_2015}. It has the least graphitic structure when compared to ACH and hemp fibers. Loosely held structures, which disintegrated rapidly after every cycle resulted in reduced capacity and low coulombic efficiency values.

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/hempmech}
    \caption{Suggested mechanism for a \textbf{Al/hemp} cell. The fibers have a large pore size (2.0-2.5 \mu m) which allow the AlCl$_4^_$ to get absorbed on the cathode surface but agglomeration of carbon atoms after a few cycles reduces the active sites available for charge storage, which reduces cell's capacity after every cycle.}
  \label{figures:hempmech}
\end{figure}
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/raman}
    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx , b) hemp fibers, c) ACH and d) Super-P cathodes indicating presence of both D and G-bands.}
  \label{figures:raman}
\end{figure}
Since it has been previously established that intercalation of \ce{AlCl4-} takes place in carbon materials during cell charge, we focused our analysis on the charged electrodes. Figure \ref{figures:raman} illustrates Raman spectra of the tested cathodes. Pristine ACH, hemp fibers and Super-P had a significant D-band indicating a distorted lattice. Increased intensity of D band can be seen in charged electrodes at ~1300 cm$^-{^1}$ (ACH), 1329.7 cm$^-{^1}$ (hemp fibers), and 1352.0 cm$^-{^1}$ (Super-P) indicating an increase in the lattice defects and deformities. Hemp fibers and ACH observed an increased FWHM (full width at half maximum) of both D and G bands indicating a loss in symmetry. Intercalation of ions or surface adsorption of anions onto the porous carbon cathode, would alter the ordered structure on the surface. We suggest capacitive intercalation mechanism as well as a redox pseudocapacitance where \ce{AlCl4-} ions electrochemically adsorb onto the surface \cite{brezesinski_ordered_2010}. 
The main feature in a fullerene Raman spectrum was a sharp line observed at 1460 cm$^-^1$, which is known as the 'pentagonal pinch mode'. \ce{C60} is composed of \ce{sp2} bonded carbon atoms. Sharpness of the band indicates a uniform nature of the bonds. However, the spectrum of C$_7_0$ has multiple bands. Reduction in its molecular symmetry increases the number of active Raman bands \cite{kimbrell_analysis_2014}. Pristine CFEx electrode observed characteristic peaks of both \ce{C60} and \ce{C70} at 1459.3 cm$^-{^1}$ and 1564 cm$^-{^1}$ respectively in Figure \ref{figures:raman}c. An interesting observation was that pristine and charged CFEx electrodes had a similar-looking spectra after cycling. Since Raman spectroscopy is sensitive to very minute differences in molecular morphology, the results suggested that the structure remained intact. Another interesting observation was made in charged ACH electrode (Figure \ref{figures:raman}a). A new peak appeared at 1466 cm$^-{^1}$. A similar band splitting was observed by Wang \textit{et al} \cite{wang_kish_2017} while charging natural graphite and AlCl$_4^-$ ions intercalated into the cathode layers. This peak appeared due to vibration of carbon atoms in a plane adjacent to intercalant layer planes. We observed no such effect was observed for any other cathode. Since the Al/ACH cell maintained a highly reversible capacity of 102 mAhg$^-^1$ after 50 cycles, we assume ACH underwent a similar mechanism, where \ce{AlCl4-} ions intercalate into the cathode during charge. ACH has a high surface area and an inter-connected mesoporosity. The layered domains present in it enable insertion of \ce{AlCl4-}, while a few anions get electrochemically adsorbed onto the surface through a charge-transfer process resulting in a redox pseudo-capacitance. All these processes seem to take place at the same time without changing the reaction kinetics. Additionally, presence of both an amorphous and crystalline structure in this material increases the charge-storage capacity of the material \cite{brezesinski_ordered_2010}. This might be the reason why ACH shows a remarkable reversibility. Schematic of a possible mechanism is shown in Figure \ref{figures:ACHmech}. Hemp fibers and Super-P had lattice deformities to begin with, which were enhanced after the cell underwent the preliminary galvanostatic cycles. This decreased capacity after every cycle. 
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/SEM}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{upgreek}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tgtermes}
\usepackage{subfig}
\usepackage[version=4]{mhchem}
\usepackage{threeparttable}
\onehalfspacing
\graphicspath{figures/}
\usepackage{array, booktabs}
\setlength{\arrayrulewidth}{0.5mm}
\setlength{\tabcolsep}{8pt}
\renewcommand{\arraystretch}{1.5}
\title{Carbon cathodes for rechargeable aluminium-ion batteries}
\author{
  Shalini Divya\\
  School of Chemical and Physial Sciences\\
  Victoria University of Wellington\\
  Wellington, New Zealand\\
  \texttt{shalini.divya@vuw.ac.nz}\\
  %% examples of more authors
   \And
  Thomas Nann\thanks{Corresponding author.}\\
  School of Mathematical and Chemical Sciences\\
  The University of Newcastle\\
  Newcastle, NSW 2308, Australia\\
  \texttt{thomas.nann@newcastle.edu.au}\\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
\maketitle
\begin{abstract}
 In this work, we compare four different forms of carbon: activated carbon from human hair, activated carbon from hemp fibers, a fullerene mixture consisting of \ce{C60} and \ce{C70} fullerenes (CFEx) and Super-P carbon black (SPCB) as cathodes for non-aqueous aluminium-ion batteries. These materials differ in their general structure, porosity and morphology. The fullerenes display a crystalline structure, whereas hemp fibers, Super-P and ACH are amorphous in nature. Of all materials, ACH recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\% at a current rate of 50 mV s$^{-1}$. Both hemp fibers and SPC achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^{-1}$ respectively. CFEx recorded its highest capacity at 78 mAh g$^{-1}$ and maintained it for 50 cycles. The cells were charged and discharged to 2.45 V and 0.2 V respectively. 
 \end{abstract}

% keywords can be removed
\keywords{carbon-based cathodes \and aluminium-ion battery \and ionic liquid \and human hair \and fullerene extract \and hemp fibers \and Super-P}

\section{Introduction}
Different varieties of carbon-based materials have been widely used in energy storage applications. Graphite, with its layered structure turned out to be an ideal intercalation cathode material \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}. Activated carbon, owing to its porous structure, provides a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011}. Aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium. Thus, they offer an interesting potential long-term alternative to the problematic LIB technology \cite{ambroz_trends_2017-1}. In this work, we tested a number of rechargeable AIBs using an ionic liquid electrolyte with different carbon-based cathodes. The aim of this study was to systematically explore the properties of different carbon-materials when used as AIB cathodes.

Graphite has been commonly used as a cathode in AIBs. It has a layered structure that enhances the intercalation process, good conductivity, and a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V. Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing typical specific capacities ranging from 60-250 mAh g$^{-1}$. The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge. X-ray diffraction (XRD) and Raman spectroscopy studies have widely been used to establish this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017, lin_ultrafast_2015} as shown in Figure \ref{SF:graphitemech}. Raman data showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation. XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively \cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.

\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/graphitemech}
    \caption{Intercalation of \ce{AlCl4-} ions while cell charging and deintercalation during discharge in a Al/graphite cell. The interlayer distance between two graphite sheets is 3.3 \AA.}
  \label{SF:graphitemech}
\end{figure}

In this study, we compared four carbon-based materials with carbonised natural products. Super-P carbon has been used consistently as an additive to overcome conductivity loss in the active electrode material (for example, when a polymer binder such as polyvinylidene fluoride (PVDF) is added to it). Using it as an active material, we tried to find if Super-P contributes any capacity of its own to the battery's specific capacity. Activated carbon from natural products like rice or wood have been previously used in super-capacitors \cite{hussain_development_2019, frackowiak_carbon_2001}. Also known as 'hierarchical porous carbons', these structures contained pores of various sizes (mesopores and micropores), which enhanced the charge storage capacity by increasing the surface area of the electrodes. The pores absorb the charge carriers reversibly on their surface. Based on this hypothesis, we used activated carbon from human hair and hemp fibers as cathodes.

@@

\begin{table}[tbh!]
\caption{Comparing average battery metrics of carbon cathodes} \label{table1}
\begin{center}
\begin{tabular}{|lcccc|}
\hline
Active material & {\textbf{Size}} & {\textbf{Specific capacity}} & {\textbf{Cell efficiency}} & {\textbf{Cell voltage}}\\
 & {\textbf{(pore size)}} & {\textbf{(mAh g$^{-1}$)}} & {\textbf{(\%)}} & {\textbf{(V)}}\\
\hline
Human hair & 5${\mu}$ m & 102 & 97 & 1.9 \\
Fullerene mix & 8.8 \AA & 78 & 85 & 1.7 \\
Hemp fibers & 2.3 $\mu$ m & 49 & 75 & 1.8 \\
SPCB & 300 \AA & 46 & 40 & 1.5 \\
\hline  % Please only put a hline at the end of the table
\end{tabular}
\end{center}
\end{table}

\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CDCall}
    \caption{Specific capacities in the a) 1$^{st}$ and b) 50$^{th}$ cycle of human hair, hemp fiber, CFEx and SPCB cathodes at a current rate of 50 mA g$^{-1}$. c) Cell efficiencies of cells at a current rate of 50 mAg$^{-1}$. d) Specific capacities of carbon cells at current rates of 25 mAg$^{-1}$, 50 mAg$^{-1}$ and 100 mAg$^{-1}$ in a two-electrode setup against Al$^{3+}$/Al. }
  \label{figures:CDCall}
\end{figure}

Our battery system comprised a cathode, 99\% pure aluminium foil as an anode, and a room temperature ionic liquid (RTIL) acting as the electrolyte. ACH, hemp fibers and Super-P had an amorphous structure, however Raman spectra confirmed the presence of a few graphitic planes. Any number of graphite-like layers would allow \ce{AlCl4-} ions to intercalate when the cell was charged. However, CFEx, a mixture of \ce{C60} and \ce{C70} fullerenes, had crystalline character. Intercalation of aluminium into the fullerene cages was not observed. We suggest that \ce{AlCl4-} anions migrated through the gaps present in between fullerenes without altering the molecular structure. Using a \textit{Neware BTS 3000} battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^{-1}$ (cf.\ Figure \ref{figures:CDCall}a and b). Structural changes in the cathode before and after the cycles were studied using Raman spectra, XRD spectra and scanning electron microscopy (SEM) images.

Figure \ref{figures:CDCall}a and b compares the specific capacities of all cells recorded in their 1$^{st}$ and 50${^th}$ cycles. Cells made of human hair displayed the highest capacity at around 100 mAh g$^{-1}$ with a coulombic efficiency at $\sim$95$\%$. High surface area due to the porous structure of the materials might have led to a additional 'capacitor-like' charge storage \cite{frackowiak_carbon_2001}. Hemp cells displayed a capacity of 56 mAh g$^{-1}$ in their first cycle, which decreased to 45 mAh g$^{-1}$ after 50 cycles. CFEx cells displayed a capacity of around 80 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\%. With an initial capacity of 84 mAh g$^{-1}$, specific capacity of SPCB cells decreased to 47 mAh g$^{-1}$ and a low coulombic efficiency at around 40\% was recorded. Capacity for SPCB and hemp cells decreased considerably after repeated charge/discharge cycles. A low coulombic efficiency (observed in both hemp and SPCB cells) can be attributed to parasitic reactions of the battery. These can include electrode or electrolyte interactions with impurities, or degradation of the cathode structure (pulverisation) \cite{gyenes}. However, capacity fade for CFEx and human hair cells was minimal. This suggest that CFEx and human hair have a more stable structure compared to hemp and SPCB and they store charge reversibly \cite{pramanick}.

% In the above paragraph, you discuss 3 specific cells. This is suicidal (metaphorically speaking). In science you make a point by showing that something is reproducible. Having done just 3 expriments is asking for the reviewer to knock it down. You need to re-write this in a more general manner.

The production of activated carbon consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonized precursor. Activating agents play an important role in determining the porosity of an activated carbon \cite{arenas}. Using alkali hydroxides, such as sodium and potassium hydroxide at high temperature creates micropores which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}. In this work, sodium hydroxide (NaOH) was used as the activating agent. The reaction that takes place inside the matrix after adding NaOH is:

\begin{center}
    4NaOH + C $\longrightarrow$ 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{satish}
\end{center}

NaOH was reduced to free metal, Na, these atoms in turn expanded the carbon matrix after intercalating into the carbon structure. Increased temperature ($\sim$900$^{\circ}$ C) forces the  atoms out of the carbon matrix, thus creating micropores. Oxidation of carbon from oxygen atoms of the hydroxide group forms \ce{CO2} providing routes for channeling the Na atoms into the internal structure leading to well-connected porous structure \cite{satish}. The calcinating temperature used here was 750$^{\circ}$ C. Figure \ref{SF:ACHsyn} displays the flowchart for activated carbon synthesis.

% Paragraph above: you need to prove/reason every statement that you make. You just claim a lot of stuff without providing any evidence. Also: ARTICLES!!!!!

%Unfortunately the structural domains appeared to have been damaged after this process. This phenomena negatively impacted its charge-storing capacity.

% Above paragraph: Lots of unnecerssary information (see comments). Focus on what is relevant. Also sentences like the Carbon Valley one are suicidal. When you write, always have your worst scientific enemy in mind and write it so that you win.

Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals diameter of 11 \AA in a single crystal. However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}. They are known to be weak battery materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}. To test their solubility in \ce{AlCl3}-EMImCl, 100 mg of CFEx was mixed in the electrolyte and stirred for 24 hours. The solution was left to stand for another 24 hours inside a \ce{N2}-filled glove box. CFEx seemed to dissolve in our electrolyte (Figure \ref{SF:CFExsol} since no phase separation was observed. It has been reported that poly-sulphides formed during cycling in a lithium-sulfur battery, are soluble in the electrolyte. They form an insulating layer of \ce{Li2S} on the anode, which results in capacity fading \cite{sun_effect_2017}. Since no such effect was observed in aluminium-fullerene cells, this phenomena does not seem to impact the charge-storing capacity of CFEx. On the contrary, the cells displayed excellent capacity retention at various current rates(Figure \ref{figures:CDCall}d).

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/superPmech}
    \caption{Suggested mechanism for a \textbf{Al/Super-P} cell. Super-P has a very amorphous structure with a few graphite-like planes present in it. \ce{AlCl4-} ions intercalate into those layers and give the cell its capacity. However, cathode pulverisation results in capacity fading.}
  \label{figures:superPmech}
\end{figure}

Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure. Its pore size ranges from $\sim$30-50 nm \cite{younesi_analysis_2015}. SPCB has the least graphitic structure if compared to human hair and hemp fibers. It seems continuous cycling might have destroyed the arrangement of the carbon atoms, which resulted in poor capacity retention and low coulombic efficiencies.

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/hempmech}
    \caption{Suggested mechanism for a \textbf{Al/hemp} cell. The fibers have a large pore size (2.0-2.5 $\mu$m) which allow the \ce{AlCl4-} to get absorbed on the cathode surface but agglomeration of carbon atoms after a few cycles reduces the active sites available for charge storage, which reduces cell's capacity after every cycle.}
  \label{figures:hempmech}
\end{figure}

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/raman}
    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx , b) hemp fibers, c) ACH and d) Super-P cathodes indicating presence of both D and G-bands.}
  \label{figures:raman}
\end{figure}

In aluminum-graphite cells, it has been established that \ce{AlCl4-} ions intercalate while charging \cite{lin_ultrafast_2015}. Since the materials we tested have graphitic planes present, we focused our analysis on the pristine and charged electrodes. Figure \ref{figures:raman} displays Raman spectra of the tested cathodes. Pristine human hair, hemp fibers and SPCB had a significant D-band present indicating absence of an ordered structure with presence of lattice defects and deformities (at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB). Figure \ref{figures:raman}c displayed the characteristic features of both \ce{C60} and \ce{C70} molecules. The 'pentagonal pinch mode', which is usually observed in a \ce{C60} Raman spectrum, was present at 1460 cm$^{-1}$. However, \ce{C70} has multiple bands. Reduction in its molecular symmetry increases the number of vibrational modes, thus increasing the active Raman bands \cite{kimbrell_analysis_2014}. Pristine CFEx cathode was composed of both \ce{C60} and \ce{C70} Raman bands as seen in Figure \ref{figures:raman}c. It was interesting to note that charged CFEx cathodes looked strikingly similar. Since Raman spectroscopy is sensitive to minute differences in the molecular morphology, results suggested that the structure remained intact after cycles. Human hair has a high surface area and an inter-connected mesoporosity. The charged cathodes showed a higher FWHM which suggests an increase in the lattice defects. Obviously, these defects arise after intercalation of chloroaluminates; it is assumed that these ions intercalate into the few graphitic planes present in the carbon matrix. In addition, a highly porous structure allows surface adsorption of charge carrying species (much like in super-capacitors) \cite{beguin_carbons_2014}. Intercalation into graphitic planes/micropores, along with surface adsorption of chloroaluminates, result in aluminium-hair batteries performing better than other materials by storing more charge\cite{brezesinski_ordered_2010}. A schematic of a possible mechanism is shown in Figure \ref{figures:ACHmech}.
%contains about 51\% carbon, 17\% nitrogen, 21\% oxygen, 6\% hydrogen, 5\% sulfur, and trace amounts of iron, magnesium, arsenic, chromium and various minerals \cite{lee_chemistry}.  
Hemp fibers and SPCB had fewer graphitic planes and a highly disordered structure to begin with. The lattice defects seemed to increase after galvanostatic cycles. Continuous intercalation or absorption of ions on their surface would have further destroyed the cathode structure. This might be the reason why hemp and SPCB cells failed to retain capacity after a few cycles. However, CFEx does not have graphitic planes. It consists of a bunch of \ce{C60} and \ce{C70} fullerenes. Insertion of \ce{AlCl4-} ions inside the cage-like structure would be thermodynamically impossible. Since the fullerenes have a very high surface area, surface adsorption of ions is likely \cite{adams}. Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes \ref{figures:CFExmech}. Capacity retention of the aluminium-CFEx cells suggests that the interaction between the fullerenes and \ce{AlCl4-} ions takes place in a systematic way.
